Enforced Invariant Confluence

### 2018-04-30 doc/paper/sections/evaluation.tex
Shrinking paper.

Lucy also includes an implementation of the \invariantconfluence{} and
segmented-invariant confluence system models in roughly 3,500 lines of C++.
Users specify objects, transactions, invariants, and segmentations in C++. Lucy
then replicates the objects using segmented \invariantconfluence{} (or
\invariantconfluence{} if the segmentation contains a single segment without
any disallowed transactions). Clients send every transaction request to a
randomly selected server. When a server receives a transaction request, it
executes \algoref{TxnExecution} to attempt to execute the transaction locally.
If the transaction requires global coordination, then the server forwards the
transaction request to a predetermined leader. When the leader receives a
transaction request, it sends a coordination request to all other servers. When
a server receives a coordination request from the leader, it stops processing
transactions and sends the leader its state in a coordination reply. When the
leader receives coordination replies from all other servers, it executes the
transaction, and then sends its state to the other servers. When a server
receives a new state, it adopts the state, computes its new active segment, and
resumes normal processing. After every 100 transactions processed, a server
sends a merge request to a randomly selected server.

>>>>

Lucy also includes an implementation of the \invariantconfluence{} and
segmented-invariant confluence system models in roughly 3,500 lines of C++.
Users specify objects, transactions, invariants, and segmentations in C++. Lucy
then replicates the objects using segmented \invariantconfluence{}. Clients
send every transaction request to a randomly selected server. When a server
receives a transaction request, it executes \algoref{TxnExecution} to attempt
to execute the transaction locally.  If the transaction requires global
coordination, then the server forwards the transaction request to a
predetermined leader. When the leader receives a transaction request, it
broadcasts a coordination request to the other servers. When a server receives
a coordination request from the leader, it stops processing transactions and
sends the leader its state. When the leader receives the states of all other
servers, it executes the transaction, and then sends its state to the other
servers. When a server receives a new state, it adopts the state, computes its
new active segment, and resumes normal processing. After every 100 transactions
processed, a server sends a merge request to a randomly selected server.

### 2018-04-30 doc/paper/sections/related_work.tex
Shrinking paper.

\textbf{Program Analysis in Database Systems.}
Using program analysis to improve the performance of database systems is not
new. For example, it has been used to improve the performance of
database-backed web applications~\cite{cheung2014using, wu2016transaction,
ramachandra2012program} and used to improve the performance of optimistic
concurrency control on multi-core machines~\cite{wu2016transaction}. Our work
on \invariantconfluence{} continues the theme of using program analysis to reap
the performance benefits gained from understanding program semantics.

>>>>

% \textbf{Program Analysis in Database Systems.}
% Using program analysis to improve the performance of database systems is not
% new. For example, it has been used to improve the performance of
% database-backed web applications~\cite{cheung2014using, wu2016transaction,
% ramachandra2012program} and used to improve the performance of optimistic
% concurrency control on multi-core machines~\cite{wu2016transaction}. Our work
% on \invariantconfluence{} continues the theme of using program analysis to reap
% the performance benefits gained from understanding program semantics.
